ECE 657A Project Report

### 2016-04-02 project report/LNCS-template/paper.tex
report latest version

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../parsing.png}
		\caption{ROC}
		\label{figure 1:Frame-Semantic Parsing}
	\end{subfigure}

@@

Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences[3].
Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../sematic.png}
		\caption{ROC}
		\label{figure 2:sematic parsing}
	\end{subfigure}

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../syntax.png}
		\caption{ROC}
		\label{figure 3:syntax}
	\end{subfigure}

@@

Comprehension with Discourse Relations[5].The model jointly identifies relevant sentences, establishes relations between them and predicts an answer. The key idea is to implant discourse analysis into a joint model for comprehension. As we could see in picture 4.And the drawback of this model is that the accuracy varies significantly according to the question type. Which means not really stable. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../disclosure.png}
		\caption{ROC}
		\label{figure 4:disclosure method}
	\end{subfigure}

@@

Comprehension for Learning Answer-Entailing Structures[6].We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text. For this given structure, the correctness of the answer is evident. Since the structure is latent, it must be inferred. Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts. We could see this from figure 5. But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../disclosure.png}
		\caption{ROC}
		\label{figure 5:answer entailing method}
	\end{subfigure}

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../LSTM.png}
		\caption{ROC}
		\label{figure 6:LSTM}
	\end{subfigure}

@@

The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query. We can go further by equipping the model with the ability to reread from the document as each query token is read. The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction. We could see figure 7 for impatient reader.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../impa.png}
		\caption{ROC}
		\label{figure 7:impatient reader}
	\end{subfigure}

@@

The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. This model could fix the bottleneck for the width of different words. This attention model first encodes the document and the query using separate bidirectional single layer LSTMs. This task has been tricky because of the number of parameters that must be fine-tuned.
Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model. We could see figure 8 for attentive model.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../attentive.png}
		\caption{ROC}
		\label{figure 8:attentive model}
	\end{subfigure}

@@

Theano is a popular choice for the implementation of neural networks (see e.g. Goodfellow et al. (2013b); Pascanu et al. (2013)). Blocks and many other libraries, such as Pylearn2 (Goodfellow et al., 2013a), build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units. In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'. 
Blocks comes with a large number of 'bricks'. 
The gradient descent training algorithm in Blocks is composed of different 'step rules' that modify the descent direction (learning rate scaling, momentum, gradient clipping, weight norm clipping, etc.). A variety of algorithms such as AdaGrad, ADADELTA, Adam, RMSProp are available as step rules. But in our project, we use gradient descent algorithm.
The goal of fuel is to provide a common interface to a variety of data formats and published datasets such as MNIST, CIFAR-10, ImageNet, etc. while making it easy for users to write an interface to new datasets. 
Blocks relies on Fuel for its data interface, but Fuel can easily be used by other machine learning frameworks that interface with datasets. 
Fuel offers built-in scripts that automate the task of downloading datasets, (similar to e.g. skdata1) and converting them to Fuel HDF5 specification. 
The fuel download script is used to download raw data files. Downloading the raw MNIST data files is as easy as typing fuel download mnist. The fuel convert script is used to convert raw data files into HDF5-format. 
Reproducibility being an important feature of both Fuel and Blocks, the fuel convert script automatically tags all files it creates with relevant module and interface versions and the exact command that was used to generate these files. Inspection of this metadata is done with the fuel info script. 
Theano is a compiler for mathematical expressions in Python that combines the convenience of NumPy syntax with the speed of optimized native machine language. The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative). These expressions allow Theano to provide symbolic differentiation. [11]
Theano was introduced to the machine learning community by Bergstra et al. (2010) as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
\section{compare of original method and the method we used}
The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. The Attentive Reader employs a finer grained token level attention mechanism where the tokens are embedded given their entire future and past context in the input document. 
The representation r of the document d is formed by a weighted sum of these output vectors. These weights are interpreted as the degree to which the network attends to a particular token in the document. Given this attention score the embedding of the document r is computed as the weighted sum of the token embeddings.

>>>>

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/parsing.png}
		\caption{ROC}
		\label{figure 1:Frame-Semantic Parsing}
	\end{subfigure}

@@

Other people also have the idea of comprehension with Syntax, Frames, and Semantics method.Semantic: frame semantic parsing (Das et al., 2014) is aimed to extract frame-specific predicate-argument structures from sentences[3].
Syntax: given each candidate answer, we attempt to transform the question to a statement using the extraction rules[4]. We could see figure 2 for sematic and figure 3 for syntax.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/sematic.png}
		\caption{ROC}
		\label{figure 2:sematic parsing}
	\end{subfigure}

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/syntax.png}
		\caption{ROC}
		\label{figure 3:syntax}
	\end{subfigure}

@@

Comprehension with Discourse Relations[5].The model jointly identifies relevant sentences, establishes relations between them and predicts an answer. The key idea is to implant discourse analysis into a joint model for comprehension. As we could see in picture 4.And the drawback of this model is that the accuracy varies significantly according to the question type. Which means not really stable. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
		\caption{ROC}
		\label{figure 4:disclosure method}
	\end{subfigure}

@@

Comprehension for Learning Answer-Entailing Structures[6].We posit that there is a hidden (latent) structure that explains the relation between the question, correct answer, and text. For this given structure, the correctness of the answer is evident. Since the structure is latent, it must be inferred. Firstly, we should presents a unified max-margin framework that learns to find these hidden structures (given a corpus of question-answer pairs), and then uses what it learns to answer machine comprehension questions on novel texts. We could see this from figure 5. But the drawback of this method is that since inference is cheaply modelled via alignment structure, we lack the ability to deeply reason about facts or numbers. 
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/disclosure.png}
		\caption{ROC}
		\label{figure 5:answer entailing method}
	\end{subfigure}

@@

\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/LSTM.png}
		\caption{ROC}
		\label{figure 6:LSTM}
	\end{subfigure}

@@

The Impatient Reader focuses on the passages of a context document that are most likely to inform the answer to the query. We can go further by equipping the model with the ability to reread from the document as each query token is read. The result is an attention mechanism that allows the model to recurrently accumulate information from the document as it sees each query token, ultimately outputting a final joint document query representation for the answer prediction. We could see figure 7 for impatient reader.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/impa.png}
		\caption{ROC}
		\label{figure 7:impatient reader}
	\end{subfigure}

@@

The Attentive Reader can be viewed as a generalization of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. This model could fix the bottleneck for the width of different words. This attention model first encodes the document and the query using separate bidirectional single layer LSTMs. This task has been tricky because of the number of parameters that must be fine-tuned.
Although this method cannot be backwards checking as impatient reader but according to some article, these two methods have the similar results, so our group used this model. We could see figure 8 for attentive model.
\begin{figure}[p]
	\centering
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=1\linewidth]{../pic/attentive.png}
		\caption{ROC}
		\label{figure 8:attentive model}
	\end{subfigure}

@@

Theano is a popular choice for the implementation of neural networks (see e.g. Goodfellow et al. (2013b); Pascanu et al. (2013)). Blocks and many other libraries, such as Pylearn2 (Goodfellow et al., 2013a), build on Theano by providing reusable components that are common in neural networks, such as linear transformations followed by non-linear activations, or more complicated components such as LSTM units. In Blocks these components are referred to as 'bricks' or 'parametrized Theano operations'. 
Blocks comes with a large number of 'bricks'. 
The gradient descent training algorithm in Blocks is composed of different 'step rules' that modify the descent direction (learning rate scaling, momentum, gradient clipping, weight norm clipping, etc.). A variety of algorithms such as AdaGrad, ADADELTA, Adam, RMSProp are available as step rules. But in our project, we use gradient descent algorithm.
The goal of fuel is to provide a common interface to a variety of data formats and published datasets such as MNIST, CIFAR-10, ImageNet, etc. while making it easy for users to write an interface to new datasets. 
Blocks relies on Fuel for its data interface, but Fuel can easily be used by other machine learning frameworks that interface with datasets. 
Fuel offers built-in scripts that automate the task of downloading datasets, (similar to e.g. skdata1) and converting them to Fuel HDF5 specification. 
The fuel download script is used to download raw data files. Downloading the raw MNIST data files is as easy as typing fuel download mnist. The fuel convert script is used to convert raw data files into HDF5-format. 
Reproducibility being an important feature of both Fuel and Blocks, the fuel convert script automatically tags all files it creates with relevant module and interface versions and the exact command that was used to generate these files. Inspection of this metadata is done with the fuel info script. 
Theano is a compiler for mathematical expressions in Python that combines the convenience of NumPy syntax with the speed of optimized native machine language. The user composes mathematical expressions in a high-level description that mimics NumPy syntax and semantics, while being statically typed and functional (as opposed to imperative). These expressions allow Theano to provide symbolic differentiation. [11]
Theano was introduced to the machine learning community by Bergstra et al. (2010) as a CPU and GPU mathematical compiler, demonstrating how it can be used to symbolically define mathematical functions, automatically derive gradient expressions, and compile these expressions into executable functions that outperform implementations using other existing tools[12].
\section{compare of original method and the method we used}
For preprocessing part:
1) split the story dataset into one story one file, and do the same thing on the related answer dataset 
2) label correct answers obtained from corresponding answer file
in each story file 
3) convert ‘n’t’ to ‘not’ using Regular Expression and numbers to words using a recrusive function implemented by ourselves on story, questions and answers in each story file 
4) lowercase all text of stories, tokenize them, then build a vocabulary file without repeat words
5) find out entities in each story and replace them with entity identifiers, then add the corresponding entity and entity identifier list below the questions
6) delete punctuations on the text of each story, the reason for doing this after step 5 is that punctuations will help to identify the entities 
7) remove stop words, lemmatization and stemming on each story dealing with NLTK library functions
8) preprocess both questions and answers using the entity list gained from step 5

The Attentive Reader can be viewed as a generalisation of the application of Memory Networks to question answering. That model employs an attention mechanism at the sentence level where each sentence is represented by a bag of embeddings. The Attentive Reader employs a finer grained token level attention mechanism where the tokens are embedded given their entire future and past context in the input document. 
The representation r of the document d is formed by a weighted sum of these output vectors. These weights are interpreted as the degree to which the network attends to a particular token in the document. Given this attention score the embedding of the document r is computed as the weighted sum of the token embeddings.
